Geometric models reveal the hidden structure of conceptual knowledge

### 2023-01-20 paper/main.tex
oops-- another typo fix

Participants began the main experiment by answering a battery of 10 randomly
selected questions (chosen from the full set of 30). Then they watched the
\textit{The Four Fundamental Forces} video. Next, they answered a second set of
10 questions (chosen at random from the remaining 20 questions). Fourth,
participants watch the \textit{Birth of Stars} video, and finally they answered
the remaining 10 questions. Our experimental procedure is diagramed in
Figure~\ref{fig:experiment}. We used the experiment to develop and test our
computational framework for estimating knowledge and learning maps.

>>>>

Participants began the main experiment by answering a battery of 13 randomly
selected questions (chosen from the full set of 39). Then they watched the
\textit{The Four Fundamental Forces} video. Next, they answered a second set of
13 questions (chosen at random from the remaining 20 questions). Fourth,
participants watch the \textit{Birth of Stars} video, and finally they answered
the remaining 13 questions. Our experimental procedure is diagramed in
Figure~\ref{fig:experiment}. We used the experiment to develop and test our
computational framework for estimating knowledge and learning maps.
